Java Based Memory Latency Simulator

### 2020-11-21 finalPaper/paper.tex
Some proofreading and updated refs

\subsection{Acquiring Source Code}
To download the simulator code, go to \url{osfinal.dachenhausen.org} 
or
\url{https://github.com/adamdachenhausen/cs330FinalProject} 
and clone the repository. See \url{https://docs.github.com/en/free-pro-team@latest/github/creating-cloning-and-archiving-repositories/cloning-a-repository}
for more.

@@

\subsection{Running the Simulator}
\begin{itemize}
\item \textbf{Command Line}
  Either way that the simulator was compiled, the command
\begin{verbatim}
  java memSim
\end{verbatim}
  will start the simulator
\item \textbf{IDE}
  Given the multitude of IDEs that are available, please see your
  specific IDE's manual for how to compile and run the simulator.
\end{itemize}
Upon running the simulator, you will be prompted for a variety of 
simulator parameters. Each of these is crucial, and cannot be left blank.

The first thing the simulator will ask you is
{\singlespace
\begin{verbatim}
Is this text blue? Y/n
\end{verbatim}
If your terminal supports ANSI colored text, then the question should be blue,
and you should respond Y. This helps point out important data.
If your terminal does not support the colored text, then you will see something like
{\singlespace
\begin{verbatim}
[34mIs this text blue? [0m Y/n
\end{verbatim}
in which case, if you respond n, the simulator will not use any ANSI text and
everything will print normally.

@@

\subsection*{Create A New System}
If you opt to create a new system, you will be presented with the prompt shown below,
which has sample data included. Note: very large numbers will make the simulator lag
the Java virtual machine, so please be careful when inputting this data.
{\singlespace
\begin{verbatim}
How many Hard Drives would you like?
1
And how big (in bytes) should each one be?
1024
How many RAM sticks would you like?
1
And how big (in bytes) should each one be?
512
How big (in bytes) would you like your CPU cache to be?
32
How long would you like it to take in seconds, to read/write to the cache?
0
How long would you like it to take in seconds, to read/write to the RAM?
5
Finally, how long would you like it to take in seconds, to read/write to a HDD?
10

***********System Config**********
1 number of hard drives, each 1024 bytes big.
1 sticks of RAM, each 512 bytes big.
CPU cache is 32 bytes big.
Cache delay is: 0seconds
RAM delay is:   5seconds
HDD delay is:   10seconds
**********************************
\end{verbatim}
}
After setting up the simulator, the components will each start up, and
you will be prompted to choose an option from the menu. You can choose to either
select based on the menu number, or the name.
{\singlespace
\begin{verbatim}
Please enter the number of your selection: 1
What would you like to do next?
1.      Move Data
2.      Read Data
3.      Write Data
4.      Delete Data
5.      Help
6.      Exit
\end{verbatim}
}

@@

\begin{tabular}{|l|r|r|}
  \hline
  HDD & Cheetah 15K.5 & Barracuda\\
  \hline
  Capacity & 300 GB & 1 TB\\
  \hline
  RPM & 15,000 & 7,200\\
  \hline
  Average Seek & 4 ms & 9ms\\
  \hline
  Platters & 4 & 4\\
  \hline
  T I/O Random & 6 ms & 13.2 ms\\
  \hline
  T I/O Sequential & 800 ms & 900 ms
  \hline
\end {tabular}

## In our simulation ##

>>>>

\subsection{Acquiring Source Code}
To download the simulator code, go to \url{osfinal.dachenhausen.org}
or \url{https://github.com/adamdachenhausen/cs330FinalProject} and clone the repository.
See \url{https:docs.github.com/en/free-pro-team@latest/github/
creating-cloning-and-archiving-repositories/cloning-a-repository} for more.

@@

\subsection{Running the Simulator}
\begin{itemize}
\item \textbf{Command Line}
  Either way that the simulator was compiled, the command
{\singlespace
\begin{verbatim}
  java memSim
\end{verbatim}
}
  will start the simulator
\item \textbf{IDE}
  Given the multitude of IDEs that are available, please see your
  specific IDE's manual for how to compile and run the simulator.
\end{itemize}
Upon running the simulator, you will be prompted for a variety of 
simulator parameters. Each of these is crucial, and cannot be left blank.

The first thing the simulator will ask you is
{\singlespace
\begin{verbatim}
Is this text blue? Y/n
\end{verbatim}
}
If your terminal supports ANSI colored text, then the question should be blue,
and you should respond Y. This helps point out important data.
If your terminal does not support the colored text, then you will see something like

\begin{verbatim}
[34mIs this text blue? [0m Y/n
\end{verbatim}
in which case, if you respond n, the simulator will not use any ANSI text and
everything will print normally.

@@

\subsection*{Create A New System}
If you opt to create a new system, you will be presented with the prompt shown below,
which has sample data included. Note: very large numbers will make the simulator lag
the Java virtual machine, so please be careful when inputting this data.
{\singlespace
\begin{verbatim}
How many Hard Drives would you like?
1
And how big (in bytes) should each one be?
1024
How many RAM sticks would you like?
1
And how big (in bytes) should each one be?
512
How big (in bytes) would you like your CPU cache to be?
32
How long would you like it to take in seconds,
 to read/write to the cache?
0
How long would you like it to take in seconds,
 to read/write to the RAM?
5
Finally, how long would you like it to 
take in seconds, to read/write to a HDD?
10
\end{verbatim}
\begin{verbatim}
***********System Config**********
1 number of hard drives, each 1024 bytes big.
1 sticks of RAM, each 512 bytes big.
CPU cache is 32 bytes big.
Cache delay is: 0seconds
RAM delay is:   5seconds
HDD delay is:   10seconds
**********************************
\end{verbatim}
}
After setting up the simulator, the components will each start up, and
you will be prompted to choose an option from the menu. You can choose to either
select based on the menu number, or the name.
{\singlespace
\begin{verbatim}
Please enter the number of your selection: 1
What would you like to do next?
1.      Move Data
2.      Read Data
3.      Write Data
4.      Delete Data
5.      Help
6.      Exit
\end{verbatim}
}

@@

\begin{tabular}{|l|r|r|}
  \hline
  HDD & Cheetah 15K.5 & Barracuda\\
  \hline
  Capacity & 300 GB & 1 TB\\
  \hline
  RPM & 15,000 & 7,200\\
  \hline
  Average Seek & 4 ms & 9ms\\
  \hline
  Platters & 4 & 4\\
  \hline
  T I/O Random & 6 ms & 13.2 ms\\
  \hline
  T I/O Sequential & 800 ms & 900 ms\\
  \hline
\end {tabular}

\subsection*{In our simulation}
